---
title: "Brein & Cognitie"
author: "Micha de Groot (10434410) & Roan de Jong (10791930)"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

## ANSWER SECTION


### Q1 Try _?log_ to read how to use log function. What are the two ways to calculate the log of 10 using base 10?


```{r}
log10(200)
log(200)/log(10)
log(200, base=10)
```

### Q2 if you assing an integer value to a variable ( e.g. k = 1), will the data value also be integer


```{r}
k = 1
is.integer(k) # No
```

### Q3 the __seq__ function is very useful ot make sequences of numbers, which will be saved as vectors. Look up how __seq__ works and make a sequence starting at 0 ending at 100 in steps of 2?


```{r}
x = seq(from=0, to=100, by=2)
x
```

### Q4 find the minimum and maximum of the random numbers you just generated, and also the position in the list


```{r}
set.seed(777)
rr = runif(100, 0, 1)

max(rr)
which.max(rr)
min(rr)
which.min(rr)
```

### Q5 try to plot all random numbers using __plot()__ and identify the min and max in it using __abline()__ to add (h)orizontal and (v)ertical lines
(hint: use ?plot and ?abline)


```{r}
plot(rr)
abline(lsfit(1:100, rr))
```

### Q6 Below are two lists, can you combine them using __rbind__, if not, why not and how could you change that?
L1 and L2 do not have the same dimensions. This can be fixed by transposing either of the two.


```{r}
L1 = matrix( c(2, 4, 3, 1, 5, 7), nrow=2, ncol=3, byrow = TRUE)
L2  = matrix( c(2, 4, 3, 1, 5, 7), nrow=3, ncol=2, byrow = F)
rbind(L1, t(L2))
```

### Q7  can you now select all cars that drove more that 30 kilometers in distance?

```{r}
twenties = subset(cars, cars$speed==20)

thirties_above = subset(cars, cars$dist>=30)
thirties_above
```

### Q8  can you use ifelse to tell for each element in the following list if it is even or odd ? (hint modulo: x %% y)

```{r, eval=T}
a = c(5,7,2,9)
ifelse(a%%2,'odd', 'even')
```
